### 2014-12-11 paper.tex
commit to pull

 \subsection{Redistricting Processes}
Taking in the states with at least 10 congressional districts, using both compactness and vote efficiency as a metric for measuring gerrymandering, we also find that purely legislative processes for redistricting produce more  
  \section{Discussion}

>>>>

 \subsection{Redistricting Processes}
Taking in the states with at least 10 congressional districts, using both compactness and vote efficiency as a metric for measuring gerrymandering, we also find that purely legislative processes for redistricting produce more gerrymandered districts.   
  \section{Discussion}
